R Notebook

### 2021-08-17 gc_ramp_comparison.Rmd
plot final

```{r}
p_bame_asymmetry <- peak_analysis %>% 
  filter(!is.na(`Asymmetry (EP)`)) %>% 
  ggplot() +
  aes(x = `Asymmetry (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Asymmetry Versus Ramp Rate") +
  xlab("Asymmetry (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_asymmetry
```

>>>>

```{r, dpi=300}
p_bame_asymmetry <- peak_analysis %>% 
  filter(!is.na(`Asymmetry (EP)`)) %>% 
  ggplot() +
  aes(x = `Asymmetry (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Asymmetry Versus Ramp Rate") +
  xlab("Asymmetry (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_asymmetry
```
